Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model

### 2023-03-23 src/docs_paper/paper.Rmd
Clarification about removing T2 and T3

@eaton2021naomi specify a joint model linking three small-area estimation models and defined over three time points: $T_1$ the time of the most recent household survey with HIV testing; $T_2$, the current time period; and $T_3$, a short term projection period.
We consider a simplified version defined only at $T_1$ omitting nowcasting and temporal projection, as these time points involve only projection and no further inference.
An overview of this simplified model is given below, highlighting the aspects which make it a challenge for existing inferential approaches.
A more complete mathematical description, as well as a \textsf{C++} template for the log-posterior, are provided in the appendix.

>>>>

@eaton2021naomi specify a joint model linking three small-area estimation models and defined over three time points: $T_1$ the time of the most recent household survey with HIV testing; $T_2$, the current time period; and $T_3$, a short term projection period.
We consider a simplified version defined only at $T_1$ omitting nowcasting and temporal projection, as these time points involve no further inference.
An overview of this simplified model is given below, highlighting the aspects which make it a challenge for existing inferential approaches.
A more complete mathematical description, as well as a \textsf{C++} template for the log-posterior, are provided in the appendix.
